The fraction of polar aligned circumbinary disks

### 2025-04-14 src/tex/response.tex

    \begin{response}{
        L615: Unclear what "1/s" means. Below a second per calculation/timestep? Please specify.
    }
        We have clarified that this refers to the time to run a single simulation until it can be determined if the third body is undergoing circular precession or libration.
    \end{response}

    \begin{response}{
        L628: Sections (missing s).
    }
    This has been fixed.
    \end{response}

    \begin{response}{
        L642: At the end of the conclusions (or else at the end of the discussion), a brief discussion on how future observations could test these findings would add value to the article.
    }
        We have added a discussion about the possibility of confirming this work though observations. We propose a survey to measure the inclinations of disks in young eclipsing binary systems could reasonably constrain the polar fraction.
    \end{response}

    \begin{response}{
        Data Editor's Comment
    }
    Author's Response
    \end{response}

    \begin{response}
        {I. Is this a showyourwork paper? If it is then we might be missing files necessary to properly augment the final article with code links. And we would need to add a paragraph to the text explaining the showyourwork icons. Would you contact the Data Editors helpdesk if you need assistance ensuring that the showyourwork elements show up in the final article. }

    \end{response}

    \begin{response}
        {
            II. I don't see the Zenodo DOI results tagged in the text. Can that be added using the instructions here: \url{https://journals.aas.org/aastexguide/#datasets}
        }
    \end{response}

    \begin{response}
        {
            III. For Showyourwork papers, we would like to you to freeze the final final version on GitHub and add that Zenodo DOI to the text as well. More information is here: \url{https://journals.aas.org/aastexguide/#datasets}

            [2] \url{https://journals.aas.org/data-guide/#repositories}

[3] \url{https://docs.github.com/en/repositories/archiving-a-github-repository/referencing-and-citing-content} 
        }
    \end{response}

    \begin{response}
        {
            IV. It appears you intend tedjohnson12/polar-disk-freq to be reusable software. If so we ask that you again freeze a copy of the final final version and cite that frozen copy with the final article.

[1] \url{https://journals.aas.org/policy-statement-on-software/}

[2] \url{https://journals.aas.org/data-guide/#repositories}

[3] \url{https://docs.github.com/en/repositories/archiving-a-github-repository/referencing-and-citing-content}
        }
    \end{response}

### 2025-04-14 src/tex/ms.tex
Data editor IV

In this study we use three methods, varying from purely analytic to $n$-body and statistical, to calculate $f_\text{polar}$ for a given population. In Section \ref{sec:analytic} we extend the analytic work to massive rings. Section \ref{sec:rk} 
describes the numerical integration of a set of coupled differential equations that describe the evolution of the binary-ring system in the secular approximation of the binary potential. In Section \ref{sec:reb} we treat the binary potential fully using the $n$-body code {\sc rebound} \citep{rebound}, finding only a negligible difference between this method and the much-faster secular approximation. We discuss our results in Section \ref{sec:results}, specifically looking at the effect that the binary eccentricity, relative angular momentum, and initial mutual inclination distributions have on the value of $f_\text{polar}$. Section \ref{sec:discussion} examines the consequences of our narrow-ring approximation, and discusses what considerations must be made to apply our results to an extended disk. Finally, Section \ref{sec:conclusions} describes our overall conclusions. Code \RR{that implements} the methods described in this paper is publicly available\footnote{\url{\codeurl}, or via \hfill \break \texttt{ pip install git+\codeurl} } as an installable Python package, and the scripts used to generate the figures along with the \LaTeX \space source are available\footnote{\ghurl} as well.

>>>>

In this study we use three methods, varying from purely analytic to $n$-body and statistical, to calculate $f_\text{polar}$ for a given population. In Section \ref{sec:analytic} we extend the analytic work to massive rings. Section \ref{sec:rk} 
describes the numerical integration of a set of coupled differential equations that describe the evolution of the binary-ring system in the secular approximation of the binary potential. In Section \ref{sec:reb} we treat the binary potential fully using the $n$-body code {\sc rebound} \citep{rebound}, finding only a negligible difference between this method and the much-faster secular approximation. We discuss our results in Section \ref{sec:results}, specifically looking at the effect that the binary eccentricity, relative angular momentum, and initial mutual inclination distributions have on the value of $f_\text{polar}$. Section \ref{sec:discussion} examines the consequences of our narrow-ring approximation, and discusses what considerations must be made to apply our results to an extended disk. Finally, Section \ref{sec:conclusions} describes our overall conclusions. Code \RR{that implements} the methods described in this paper is publicly available\footnote{\url{\codeurl}, or via \hfill \break \texttt{ pip install git+\codeurl} } as an installable Python package \RR{\citep[\texttt{v1.0.1}]{johnson2025a}}, and the scripts used to generate the figures along with the \LaTeX \space source are available\footnote{\ghurl} as well.
